Near and mid-infrared properties of known $z\geq5$ Quasars

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180714.tex
tex/older_tex/ removed

\title[Very high-$z$ Quasars]
        {Near and mid-infrared properties of known $z\geq5$ Quasars}
\author[Ross \& Cross]
       {Nicholas P. Ross$^{1}$\thanks{Corresponding Author: npross@roe.ac.uk} and Nicholas J. G. Cross$^{1}$
\\ 
$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
}

@@

\section*{TO DOs}
{\bf For NPR: }
\begin{itemize}
\item Almost certainly want to compile M$_{\rm BH}$; hmmmm....
\item May well wanna try and get M$_{\star}$ too...!! (yuck); 
\item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
\item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
\item Concentrate on NIR and W1/W2
\item SED dust plot with just W1/W2...
\item Check vs. Assef R90/C75 catalog.
\end{itemize}

\noindent
{\bf For NJGC: }
\begin{itemize}
\item Write the NIR data section(s) 
\end{itemize}

\noindent
{\bf For Both: }
\begin{itemize}
\item Need to decide what mags and mag system we are reporting, espeically in the 
NIR...
\item Depth/area QLF calculation to see whether the NIR surveys have been fully mined...
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Very high redshift quasars (VH$z$Q; and defined here to have redshifts
$z\geq5.00$) are excellent probes of the early Universe. This includes
studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
Volonteri2010, Agarwal2016, Valiante2018, Latif2018} and early metal
enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.

The build-up of SMBHs via accretion is important due to the desire to
understand the evolution of the black hole mass function (BHMF) and
since there is a remarkable similarity between cosmic star-formation
rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and
BHAR trace each other \citep[with a normalisation factor of
$\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts
$z=0-4$.  However, new results \citep[e.g., ][]{Vito2018a, Calhau2018}
suggest that the SFRD and BHAR do {\it not} have the same evolutionary form
at higher redshift, $z>4$. The physical reasons for this are currently very poorly
understood.  For the high-$z$ QSOs that we can measure BHAR and SFR, most
have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at
$z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g.,
][]{Netzer2014} and {\it Herschel}-detected quasars show no evolution
in the $M_{\rm BH} - M_{\star}$ relation from $z\sim2$ to $z\sim0$.
where $M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass,
stellar mass of the bulge and galaxy total stellar mass,
respectively. The evolution and potential importance of the SFRD and BHAR 
link is a key outstanding problem in contemporary astrophysics, 
potentially explaining the galaxy-black hole scaling relations. 
However, there may also simply be a non-causal origin of the black-hole 
galaxy scaling relations \citep{Jahnke2011}.

Quasars are also known to be prodigious emitters of infrared emission,
thought to be from the thermal emission of dust grains heated by
continuum emission from the accretion disc \citep[][]{Hill2014,
Hickox2017}.  Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
allow discrimination between AGN\footnote{Historically, ``quasars'' and
``Active Galactic Nuclei (AGN)'' have described different
luminosity/classes of objects, but here we use these terms
interchangeably (with a preference for quasar) in recognition of the
fact that they both describe accreting supermassive black holes
\citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the
1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g.,
][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b,
Timlin2016} as well as AGN and star-forming galaxies due to the
presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
\citep[e.g., ][]{Yan2007, Tielens2008}.

\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
a quasar without hot-dust emission in a sample of 21 $z\approx6$
quasars. Such apparently hot-dust-free quasars have no counterparts at
low redshift. Moreover, those authors demonstrate that the hot-dust
abundance in the 21 quasars builds up in tandem with the growth of the
central black hole.

WISE mapped the sky in 4 passbands, in bands centered at wavelengths
of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky
``ALLWISE'' catalog, contains nearly 750 million detections at
high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}. \citet{Assef2013},
\citet{Stern2012}. \citet{Blain2013} presented WISE mid-infrared (MIR)
detections of 17 (55\%) of the then known 31 quasars at $z >
6$. However, \citet{Blain2013} was compiled with the WISE `All-Sky'
data release, as opposed to the superior ``AllWISE'' catalogs. That
sample only examined the 31 known $z>6$ quasars; our sample has 148
objects with redshift $z \geq 6.00$.

Here we update \citet{Jiang2010} and \citet{Blain2013} \citep[along
with Table 8 of][]{Banados2016}. Our motivations are numerous and
include: {\it (i)} establishing the first complete catalogue of
$z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
reporting homogenous near-infrared photometry for the quasars; {\it
(iii)} making the first study of NIR variability of the VHzQ
population and {\it (iv)} establishing the photometric properties for
upcoming surveys and telescopes, e.g. the Large Synoptic Survey
Telescope (LSST) \footnote{\href{https://www.lsst.org}{{lsst.org}}},
ESA {\it
Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}}
and the {\it James Webb Space Telescope}
(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};
\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};
\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};
\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}

We chose redshift $z=5.00$ as our lower redshift limit due to a combination 
of garnishing a large sample, adequately spanning physical properties 
(e.g. luminosity, age of the Universe) and to incorporate what knowledge 
we've gained over the last couple of decades since $z>5$ quasars were 
discovered.

@@

Because of established conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4 magnitudes are calibrated on the Vega system (Wright et al. 2010). For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011, Brown2014b}. \citet{Brown2014b}, in PASA, is the paper about Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4 Filter. We make use of the Explanatory Supplement to the WISE All-Sky Data Release, as well as the WISE AllWISE Data Release  Products online. 
All optical ($ugriz$ bands) magnitudes are given in the AB system. 
{\bf Need to decided 
All near-infrared  ($y/YJHK$) are also given in the AB system.

We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$,  $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016) in order to be consistent with \citet{Banados2016}.

@@

\begin{table}
\begin{tabular}{l r l}
\hline  \hline
Survey   & \# VH$z$Qs & Notes  \\
\hline  
  ATLAS      &    4    &  \\
  CFHQS     &  20    &  \\
  DELS        &    2    &  \\
  ELAIS       &    1    &  \\
  FIRST       &    1    &  \\
  HSC         &    8    &  \\
  IMS          &   1     &  \\
  MMT        &  12    &  \\
  NDWFS    &  1      &  \\
  PSO          &    84  & \\
  RD           &  1       & \\
  SDSS        & 156       & \\
  SOUV       & 20       & \\
  SDWISE    & 27& \\
  SHELLQs  & 55 & \\
  ULAS       & 10& \\
  VDES       & 11& \\
  VIK          & 9 &\\
  VIMOS     & 1& \\
\hline  \hline
\end{tabular}
\caption{ATLAS \citet{Shanks2015}; }
      \label{tab:surveys}
\end{table}

@@

Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
\citet{Jiang2008}, \citet{Wang2008}, \citet{Jiang2009}, \citet{Kurk2009}, 
\citet{Mortlock2009}, \citet{Willott2009}, \citet{Carilli2010}, 
\citet{Wang2010}, \citet{Willott2010a}, \citet{Willott2010b}, 
\citet{DeRosa2011}, \citet{Mortlock2011}, \citet{Wang2011}, 
\citet{Zeimann2011}, \citet{Morganson2012}, \citet{Venemans2012}, 
\citet{McGreer2013}, \citet{Venemans2013}, \citet{Wang2013}, 
\citet{Willott2013b}, \citet{Banados2014}, \citet{Calura2014}, 
\citet{Leipski2014}, \citet{Banados2015a}, \citet{Banados2015b}, 
\citet{Becker2015}, \citet{Carnall2015}, \citet{Jiang2015}, 
\citet{Kashikawa2015}, \citet{Kim2015}, \citet{Reed2015}, 
\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Willott2015}, 
\citet{Wu2015}, \citet{Venemans2016}, \citet{Wang2016_WISE}, 
\citet{Matsuoka2016}, \citet{WangR2016}, \citet{Mortlock2011},
\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a} 
and \citet{Matsuoka2018b}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}
\label{sec:conclusions}
In this study, we have, for the first time, ompiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects, given their detection rates and SEDs. We find that:

\begin{itemize}
    \item Lorem ipsum dolor sit amet, consectetur adipiscing
      elit. Aliquam porta sodales est, vel cursus risus porta non. Vivamus
      vel pretium velit. Sed fringilla suscipit felis, nec iaculis lacus
      convallis ac. 
    \item Fusce pellentesque condimentum dolor, quis vehicula
      tortor hendrerit sed. Class aptent taciti sociosqu ad litora torquent
      per conubia nostra, per inceptos himenaeos. Etiam interdum tristique
      diam eu blandit. Donec in lacinia libero.
    \item Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
      pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
      id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
      dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
      euismod. Cras vel auctor neque. Nam quis diam risus.
\end{itemize}
Nunc lacus nibh, convallis ac lobortis ut, tempus ac lectus. Maecenas
eu elit massa. Nulla vel lacus lorem. Proin et lobortis
tortor. Phasellus ultrices nisl non enim porttitor dictum. Curabitur
nec nunc ac nibh ornare elementum. Nunc ultrices hendrerit
ultricies. Aliquam dapibus semper est et gravida. Etiam cursus, massa
eget tempor elementum, lectus urna feugiat nisi, eget sagittis.

@@

\section{A. Photometric Bands and Conversions}
    Due to the differing normalizations between the
    SDSS and  UKIDSS photometric systems, certain corrections are required.  To present
    our data in the  purest sense, all the NIR magnitudes from UKIDSS
    (originally AB magnitudes)  were corrected to Vega magnitudes as
    suggested in \citet{Hewett06}.

    Although ULAS magnitudes are reported in terms of Vega and SDSS
    magnitudes are reported in AB terms for the most part whenever an
    optical-NIR color was calculated both magnitudes were left in their
    default term.

\begin{table*}[h*]
  \begin{center}
   \caption{Adapted from Table 9 of \citet{Peth11}. 
CTIO/DECam, PanSTARRS/PS1, LSST
%References: www.cfht.hawaii.edu/Instruments/Filters/wircam.html
Filter only values. 
}
    \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lcllcl}
      \hline
      \hline
      Band & $\lambda_{\rm eff}  {\buildrel _{\circ} \over {\mathrm{A}}}$ 
              &  $\lambda_{\rm min} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
              & $\lambda_{\rm max} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
              & W$_{\rm eff}$ ${\buildrel _{\circ} \over {\mathrm{A}}}$ 
              & AB - Vega Transformations \\
      \hline
%      {\it u} & 3551  &  3005 &  4000 &  581 & $u$ = $u_{AB}$ - 0.927 \\
%      {\it u_{\rm LSST}} &	3733 &	3182 &	4082 &	?? \\
      $g_{\rm LSST}$      &     4730   &	3877    &	   5665   &  1333   &  $g_{\rm LSST}      = g_{\rm AB} + x $ \\
      $g_{\rm DECam}$  &     4734   & 	3939    &    5528   &   1133   &  $g_{\rm DECam}  = g_{\rm AB} + x $ \\	     
      $g_{\rm PS1}$        &     4776   &    3943    &    5593   &   1167   &  $g_{\rm PS1}      = g_{\rm AB} + x $ \\
      $r_{\rm PS1}$         &     6130  & 	5386    &    7036   &   1318   &  $r_{\rm PS1}       = r_{\rm AB} + y $ \\
      $r_{\rm LSST}$       &     6139  &	5375    &    7055   &   1338   &  $r_{\rm LSST}      = r_{\rm AB} + x $ \\	
      $r_{\rm DECam}$   &     6345  & 	5506    &	   7238   &   1379   &  $r_{\rm DECam}  = r_{\rm AB} + x $ \\	     
      $i_{\rm PS1}$         &     7485  &     6778    &    8304   &   1243   &  $i_{\rm PS1}       = i_{\rm AB} + x $ \\
      $i_{\rm LSST}$       &     7487  &	6765    &	   8325   &   1209   &  $i_{\rm LSST}      = i_{\rm AB} + x $ \\
      $i_{\rm DECam}$   &     7750 &	6950    &    8646    &   1371   &  $i_{\rm DECam}  = i_{\rm AB} + x $ \\	   
      $z_{\rm PS1}$        &     8658 &	8028    &    9346   &      966   &  $z_{\rm PS1}     = z_{\rm AB} + y $ \\
      $z_{\rm LSST}$      &     8669 &	8035    &	   9375   &      994  &   $z_{\rm LSST}      = i_{\rm AB} + x $ \\

>>>>

\title[Very high-$z$ Quasars]
        {Near and mid-infrared properties of known $z\geq5$ Quasars}
\author[Ross \& Cross]
       {Nicholas P. Ross$^{1}$\thanks{email: npross@roe.ac.uk} and Nicholas J. Cross$^{1}$
\\ 
$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
}

@@

\section*{TO DOs}
\begin{itemize}
\item Almost certainly want to compile M$_{\rm BH}$; 
\item May well wanna try and get M$_{\star}$ too...!! ; 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Very high redshift quasars (VH$z$Qs, defined here to have redshifts
$z\gtrsim5$) are excellent probes of the early Universe. This includes
studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
Volonteri2010, Agarwal2016, Valiante2018, Latif2018} and early metal
enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.

%The build-up of SMBHs via accretion is important due to the desire to understand the evolution of the black hole mass function (BHMF) and since there is a remarkable similarity between cosmic star-formation rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and BHAR trace each other \citep[with a normalisation factor of $\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts $z=0-4$.  However, new results \citet[e.g., ][]{Vito2018a, Calhau2018} suggest that the SFRD and BHAR do not have the same evolutionary form at higher, $z>4$ redshifts, for reasons that are currently poorly understood.  For some high-$z$ QSOs we can measure BHAR and SFR: most have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at $z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g., ][]{Netzer2014}. 
%%However, we also note the potential for the non-causal origins of the
%%black-hole galaxy scaling relations \citep{Jahnke2011}.

Quasars are also known to be prodigious emitters of infrared emission,
thought to be from the thermal emission of dust grains heated by
continuum emission from the accretion disc \citep[][]{Hill2014,
Hickox2017}.  Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
allow discrimation between AGN\footnote{Historically, ``quasars'' and
``Active Galactic Nuclei (AGN)'' have described different
luminosity/classes of objects, but here we use these terms
interchangeably (with a preference for quasar) in recognition of the
fact that they both describe accreting supermassive black holes
\citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the
1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g.,
][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b,
Timlin2016} as well as AGN and star-forming galaxies due to the
presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
\citep[e.g., ][]{Yan2007, Tielens2008}.

\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
a quasar without hot-dust emission in a sample of 21 $z\approx6$
quasars. Such apparently hot-dust-free quasars have no counterparts at
low redshift. Moreover, we demonstrate that the hot-dust abundance in
the 21 quasars builds up in tandem with the growth of the central
black hole,

\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17
(55\%) of the then known 31 quasars at $z > 6$. However,
\citet{Blain2013} was compiled with the WISE `All-Sky' data release,
as opposed to the superior ``AllWISE'' catalogs. That sample only
examined the 31 known $z>6$ quasars; our sample has 148 objects with
redshift $z\geq6.00$.

Here we update \citet{Jiang2010}  and \citet{Blain2013} 
\citep[along with Table 8 of][]{Banados2016}.

We chose redshift $z=5.0$ as our lower redshift limit due to a combination 
of garnishing a large sample, adequately spanning physical properties 
(e.g. luminosity, age of the Universe) and to incorporate what knowledge 
we've gained over the last couple of decades since $z>5$ quasars were 
discovered.

WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}. \citet{Assef2013}, \citet{Stern2012}

In this paper, we introduce the ``WISE W4 Compendium'' (WW4C); a detailed study into the objects that were detected in the longest waveband, 20-28$\mu$m observed, on the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission. This study will describe all 40 million objects that are detected in the WISE W4-band, but will concentrate on those objects most affected by radiating dust emission and well described by extragalactic, and AGN, spectral energy distributions (SEDs).  The motivations of the WW4C are numerous, but the primary science we will pursue is the identification of bolometric luminous AGN, especially those that might not be observered in X-ray/UV/optical surveys. %%

\citet{Brown2014b}, in PASA, is the paper about Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4 Filter,

@@

$M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass, stellar mass of the bulge and 
 galaxy total stellar mass, respectively.

Because of established conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4 magnitudes are calibrated on the Vega system (Wright et al. 2010). For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011, Brown2014b}. We make use of the Explanatory Supplement to the WISE All-Sky Data Release, as well as the WISE AllWISE Data Release  Products online. All optical ($ugriz$ bands) magnitudes are given in the AB system, all near-infrared  ($y/YJHK$) are also given in the AB system.  We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$,  $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016) in order to be consistent with \citet{Banados2016}.

@@

@@

%% From Banado2016
%% Fan et al. (2000) [2000AJ....120.1167F];     3 = Fan et al. (2001) [2001AJ....122.2833F];     4 = Fan et al. (2003) [2003AJ....125.1649F];     5 = Fan et al. (2004) [2004AJ....128..515F];     6 = Mahabal et al. (2005) [2005ApJ...634L...9M];     7 = Cool et al. (2006) [2006AJ....132..823C];     8 = Fan et al. (2006a) [2006AJ....131.1203F];     9 = Goto et al. (2006) [2006MNRAS.371..769G];    10 = Mcgreer et al. (2006) [2006ApJ...652..157M];    11 = Carilli et al. (2007) [2007ApJ...666L...9C];   12 = Kurk et al. (2007) [2007ApJ...669...32K];    13 = Stern et al. (2007) [2007ApJ...663..677S];    14 = Venemans et al. (2007a) [2007MNRAS.376...76V];    15 = Willott et al. (2007) [2007AJ....134.2435W];    16 = Jiang et al. (2008) [2008AJ....135.1057J];    17 = Wang et al. (2008b) [2008ApJ...687..848W];    18 = Jiang et al. (2009) [2009AJ....138..305J];    19 = Kurk et al. (2009) [2009ApJ...702..833K];    20 = Mortlock et al. (2009) [2009A&A...505...97M];    21 = Willott et al. (2009) [2009AJ....137.3541W];    22 = Carilli et al. (2010) [2010ApJ...714..834C];   23 = Wang et al. (2010) [2010ApJ...714..699W];    24 = Willott et al. (2010a) [2010AJ....140..546W];    25 = Willott et al. (2010b) [2010AJ....139..906W];    26 = Derosa et al. (2011) [2011ApJ...739...56D];    27 = Mortlock et al. (2011) [2011Natur..474..616M];   28 = Wang et al. (2011) [2011ApJ...739L..34W];   29 = Zeimann et al. (2011) [2011ApJ...736...57Z];    30 = Morganson et al. (2012) [2012AJ....143..142M];    31 = Venemans et al. (2012) [2012ApJ...751L..25V];   32 = Mcgreer et al. (2013) [2013ApJ...768..105M];    33 = Venemans et al. (2013) [2013ApJ...779...24V];   34 = Wang et al. (2013) [2013ApJ...773...44W];   35 = Willott et al. (2013b) [2013ApJ...770...13W];    36 = Banados et al. (2014) [2014AJ....148...14B];    37 = Calura et al. (2014) [2014MNRAS.438.2765C];    38 = Leipski et al. (2014) [2014ApJ...785..154L];   39 = Banados et al. (2015a) [2015ApJ...805L...8B];   40 = Banados et al. (2015b) [2015ApJ...804..118B];   41 = Becker et al. (2015) [2015PASA...32...45B];    42 = Carnall et al. (2015) [2015MNRAS.451...16C];    43 = Jiang et al. (2015) [2015AJ....149..188J];    44 = Kashikawa et al. (2015) [2015ApJ...798...28K];   45 = Kim et al. (2015) [2015ApJ...813L..35K];   46 = Reed et al. (2015) [2015MNRAS.454.3952R];    47 = Venemans et al. (2015a) [2015MNRAS.453.2259V];    48 = Venemans et al. (2015b) [2015ApJ...801L..11V];   49 = Willott et al. (2015) [2015ApJ...801..123W];   50 = Wu et al. (2015) [2015Natur..518..512W];    51 = Venemans et al. (2016) [2016ApJ...816...37V];   52 = Wang-Feige et al. (2016) [labaApJ...819...24W];   53 = Matsuoka et al. (2016) [2016arXiv160302281M];   54 = Wang et al. (2016) [2016arXiv160609634W];
Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
\citet{Jiang2008}, \citet{Wang2008} \citet{Jiang2009} \citet{Kurk2009}
\citet{Mortlock2009} \citet{Willott2009} \citet{Carilli2010}
\citet{Wang2010} \citet{Willott2010a} \citet{Willott2010b}
\citet{DeRosa2011} \citet{Mortlock2011} \citet{Wang2011}
\citet{Zeimann2011} \citet{Morganson2012} \citet{Venemans2012}
\citet{McGreer2013} \citet{Venemans2013} \citet{Wang2013}
\citet{Willott2013b} \citet{Banados2014} \citet{Calura2014}
\citet{Leipski2014} \citet{Banados2015a} \citet{Banados2015b}
\citet{Becker2015} \citet{Carnall2015} \citet{Jiang2015}
\citet{Kashikawa2015} \citet{Kim2015} \citet{Reed2015}
\citet{Venemans2015a} \citet{Venemans2015b} \citet{Willott2015}
\citet{Wu2015} \citet{Venemans2016} \citet{Wang2016_WISE}
\citet{Matsuoka2016} \citet{WangR2016} , \citet{Mortlock2011},
\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a}
and \citet{Matsuoka2018b}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}
\label{sec:conclusions}
In this study, we have, for the first time, ompiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects, given their detection rates and SEDs. We find that::

\begin{itemize}
    \item{This sample spans a redshift range of $0.28 < z < 4.36$ and has a bimodal distribution, with peaks 
        at $z\sim0.8$ and $z\sim2.5$.}
   \item{We recover a wide range of quasar spectra in this selection.  
        The majority of the objects have spectra of reddened Type 1
        quasars, Type 2 quasars (both at low and high redshift) and objects
        with strong absorption features.} 
    \item{There is a relatively high fraction of Type 2 objects at low redshift,
        suggesting that a high optical-to-infrared colour can be an efficient
        selection of narrow-line quasars.}
    \item{There are three objects that are detected in the $W4$-band but
        not $W1$ or $W2$ (i.e., ``W1W2-dropouts''), all of which are at
        $z>2.6$.}
    \item{We identify an intriguing class of objects at $z\simeq 2-3$ which are
        characterized by equivalent widths of REW(C\,{\sc iv})
        $\gtrsim150$\AA.  These objects often also have unusual line
        properties.  We speculate that the large REWs may be caused by
        suppressed continuum emission analogous to Type 2 quasars in the
        Unified Model. However, there is no obvious mechanism in the Unified
        Model to suppress the continuum without also suppressing the broad
        emission lines, thus potentially providing an interesting challenge to
        quasar models.} 
\end{itemize}
Nunc lacus nibh, convallis ac lobortis ut, tempus ac lectus. Maecenas
eu elit massa. Nulla vel lacus lorem. Proin et lobortis
tortor. Phasellus ultrices nisl non enim porttitor dictum. Curabitur
nec nunc ac nibh ornare elementum. Nunc ultrices hendrerit
ultricies. Aliquam dapibus semper est et gravida. Etiam cursus, massa
eget tempor elementum, lectus urna feugiat nisi, eget sagittis

@@
